Tool-driven Revolutions in Archaeological Science

### 2020-01-22 analysis/paper/jcaa-paper.Rmd

archy_cran_cites_all_areas_top_journals_by_year_to_plot <- 
  archy_cran_cites_all_areas_top_journals_by_year # %>% 
# filter(SO != "AFRICAN ARCHAEOLOGICAL REVIEW")

all_archaeology_citing_R_over_time <-
  ggplot(archy_cran_cites_all_areas_top_journals_by_year_to_plot,
         aes(PY,
             prop,
             colour = SO)) +
  scale_color_viridis_d(option = "A") +
  scale_x_continuous(breaks = min_y:2018,
                     limits = c(min_y, max_y)) +
  scale_y_continuous(limits = c(0, 0.2)) +
  geom_line(size = 2) +
  geom_point() +
  geom_text_repel(
    data = archy_cran_cites_all_areas_top_journals_by_year_to_plot %>%
      group_by(SO) %>%
      slice(which.max(PY)) %>% 
      ungroup() %>% 
      top_n(5, total_n_articles) %>% 
      mutate(SO_n = str_wrap(SO_n, 30)),
    aes(label = SO_n),
    hjust = -1,
    direction = "y",
    size = label_text_size,
    nudge_x = 5) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.title.x = element_text(hjust = 0.4),
        legend.position="none",
        axis.text.x = element_text(angle = 90,
                                   hjust = 1,
                                   vjust = 0.5)) +
  xlab("Publication year") +
  ylab("Proportion of articles in that journal") +
  lemon::coord_capped_cart(bottom='right')

>>>>

archy_cran_cites_all_areas_top_journals_by_year_to_plot <- 
  archy_cran_cites_all_areas_top_journals_by_year %>%
  filter(total_n_articles > 5)
# %>% 
# filter(SO != "AFRICAN ARCHAEOLOGICAL REVIEW")

all_archaeology_citing_R_over_time <-
  ggplot(archy_cran_cites_all_areas_top_journals_by_year_to_plot,
         aes(PY,
             prop,
             colour = SO)) +
  scale_color_viridis_d(option = "D") +
  scale_x_continuous(breaks = min_y:2018,
                     limits = c(min_y, max_y)) +
  scale_y_continuous(limits = c(0, 0.2)) +
  geom_line(size = 2) +
  geom_point() +
  geom_text_repel(
    data = archy_cran_cites_all_areas_top_journals_by_year_to_plot %>%
      group_by(SO) %>%
      slice(which.max(PY)) %>% 
      ungroup() %>% 
      top_n(5, total_n_articles) %>% 
      mutate(SO_n = str_wrap(SO_n, 30)),
    aes(label = SO_n),
    hjust = -1,
    direction = "y",
    size = label_text_size,
    nudge_x = 5) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        axis.title.x = element_text(hjust = 0.4),
        legend.position="none",
        axis.text.x = element_text(angle = 90,
                                   hjust = 1,
                                   vjust = 0.5)) +
  xlab("Publication year") +
  ylab("Proportion of articles in that journal") +
  lemon::coord_capped_cart(bottom='right')
